Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2018-02-07 aggregation/agg-agg.tex
Starting the reviewer response

See Figure~\ref{fig:aggregation}e and f. At this level of aggregation, the entire dependency vector is replaced with an aggregated life cycle inventory vector $\tilde{\mathbf{b}}_x$ derived from the background LCIDB.  The reader no longer requires access to any background database to perform the computation, but all dependency information is concealed.  Again, foreground emissions are often not distinguished from the aggregation result (Figure~\ref{fig:aggregation}f).  The life cycle inventory $\tilde{\mathbf{b}}$ provides the most aggregated form of the study that can still be independently validated with an external characterization vector $\mathbf{c}$.

>>>>

See Figure~\ref{fig:aggregation}e and f. At this level of aggregation, the entire dependency vector is replaced with an aggregated life cycle inventory vector $\tilde{\mathbf{b}}_x$ derived from the background LCIDB.  The reader no longer requires access to any background database to perform the computation, but all dependency information is concealed.  As mentioned above, foreground emissions are often not distinguished from the aggregation result; if foreground and background emissions are added together, the disclosure is as shown in Figure~\ref{fig:aggregation}f.  The life cycle inventory $\tilde{\mathbf{b}}$ provides the most aggregated form of the study that can still be independently validated with an external characterization vector $\mathbf{c}$.

### 2018-02-07 aggregation/agg-review.tex
Change $ to $
Starting the reviewer response

Together, these lists can be considered a functional definition of the study scope that can be used to conduct a qualitative comparison of multiple studies by different authors.  Background database choice, dataset selection, and version information is all made available in disclosure item~\ref{itm:bg}, thereby streamlining what is presently an interpretive and study-specific process of extracting this information from written text.  Similarly, the set of elementary flows explicitly modeled in the study foreground (item~\ref{itm:em}) expose whether any study-specific modeling of direct emissions was performed and what flows were included.

@@

Partial aggregation is already used in practice to conceal private data, but current methods do not provide a way for a reviewer to validate the result.  If a study containing confidential information is split into public and private partitions as in Eq.~\ref{eqn:private} and Fig.~\ref{fig:private}, then the results of the computation can be validated directly by the reviewer.  To achieve this, the reviewer must be granted access to both the public and private partitions in order to confirm that the partitioning is valid according to Eq.~\ref{eqn:partition}, and that $\mathbf{b}_{priv}$ was computed correctly.  However, the private information used in the computation can still be withheld from the disclosure.

A further advantage to this approach is that the reader can evaluate easily what fraction of the overall impact score is accounted for by the public versus the private portions of the model.  A ``disclosure completeness'' metric $\varphi$ can be defined as the fraction of the overall score which is accounted for by the disclosed portion of the PSM:
\begin{equation}
  \varphi =  \frac{\mathbf{e}^T\cdot(\mathbf{b} - \mathbf{b}_{priv})}{\mathbf{e}^T\cdot\mathbf{b}} = 1 - \frac{\mathbf{e}^T\cdot\mathbf{b}_{priv}}{\mathbf{e}^T\cdot\mathbf{b}}
  \label{eqn:metric}
\end{equation}
where $\mathbf{b}$ is the complete life cycle inventory.  The value of this metric can provide an indication of the level of transparency of the disclosure with respect to a given impact category indicator.

>>>>

Together, these lists can be considered a functional definition of the study scope that can be used to conduct a qualitative comparison of multiple studies by different authors.  Background database choice, dataset selection, and version information can all be made available in disclosure item~\ref{itm:bg}, thereby streamlining what is presently an interpretive and study-specific process of extracting this information from written text.  Similarly, the set of elementary flows explicitly modeled in the study foreground (item~\ref{itm:em}) expose whether any study-specific modeling of direct emissions was performed and what flows were included.

@@

Partial aggregation is already used in practice to conceal private data, but current methods do not provide a way for a reviewer to validate the result.  If a study containing confidential information is split into public and private partitions as in Eq.~\ref{eqn:private} and Fig.~\ref{fig:private}, then the results of the computation can be validated directly by the reviewer.  To achieve this, the reviewer must be able to confirm that the partitioning is valid according to Eq.~\ref{eqn:partition}, and that $\mathbf{b}_{priv}$ was computed correctly.  This requires that the reviewer be granted access to both the public and private partitions.  However, the private information used in the computation can still be withheld from the disclosure.

A further advantage to this approach is that the reader can evaluate easily what fraction of the overall impact score is accounted for by the public versus the private portions of the model.  A ``disclosure completeness'' metric $\varphi$ can be defined as the fraction of the overall score which is accounted for by the disclosed portion of the PSM:
\begin{equation}
  \varphi =  \frac{\mathbf{c}^T\cdot(\mathbf{b} - \mathbf{b}_{priv})}{\mathbf{c}^T\cdot\mathbf{b}} = 1 - \frac{\mathbf{c}^T\cdot\mathbf{b}_{priv}}{\mathbf{c}^T\cdot\mathbf{b}}
  \label{eqn:metric}
\end{equation}
where $\mathbf{b}$ is the complete life cycle inventory.  The value of this metric can provide an indication of the level of transparency of the disclosure with respect to a given impact category indicator.
